Fail Faster

### 2025-03-15 paper/paper.tex
oops fix caps

@@

\section{evaluation}
\subsection{implementing and testing generators}
\label{subsection:pbt-for-pbt}
\jwc{talk about the difftesting to ensure staging maintains semantics, and also different rngs have identical semantics.}

\subsection{benchmarking speed \& resource usage}

\jwc{note: we should test generator speed across both languages, but speed -> bugfinding ability in only ocaml.}
\jwc{
  baseline generators to test speed in both languages:
  \begin{itemize}
    \item single int
    \item pair of ints, constrained
    \item list of ints without bind (use map): lots of sampling, minimal binds.
    \item unableled trees of a fixed size (no weighted union) minimal sampling, lots of binds.
  \end{itemize}
}
\subsection{impact on bug-finding ability}
\jwc{staging type-derived generators (which are the most commonly used ones) can turn a timeout into a found bug!}
\section{conclusion \& future work}
\section{related work}
\jwc{a generator is a parser of randomness, and people have implemented lots of staged parser libraries!}
%%
%% the next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{acm-reference-format}
\bibliography{bib}

%%
%% if your work has an appendix, this is the place to put it.
\end{document}
\endinput
%%
%% end of file `sample-sigplan.tex'.

>>>>

\label{subsection:faster-rng}

@@

\section{Evaluation}
\subsection{Implementing and Testing Generators}
\label{subsection:pbt-for-pbt}
\jwc{Talk about the difftesting to ensure staging maintains semantics, and also different RNGs have identical semantics.}

\subsection{Benchmarking speed \& resource usage}

\jwc{NOTE: we should test generator speed across both languages, but speed -> bugfinding ability in only OCaml.}
\jwc{
  Baseline generators to test speed in both languages:
  \begin{itemize}
    \item Single int
    \item Pair of ints, constrained
    \item List of ints without bind (use map): lots of sampling, minimal binds.
    \item Unableled Trees of a fixed size (no weighted union) minimal sampling, lots of binds.
  \end{itemize}
}
\subsection{Impact on bug-finding ability}
\jwc{Staging type-derived generators (which are the most commonly used ones) can turn a timeout into a found bug!}
\section{Conclusion \& Future Work}
\section{Related Work}
\jwc{A generator is a parser of randomness, and people have implemented lots of staged parser libraries!}
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

%%
%% If your work has an appendix, this is the place to put it.
\end{document}
\endinput
%%
%% End of file `sample-sigplan.tex'.
